---
title: "assign4"
output: html_notebook
---

For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

# Part 1

```{r}
library(lubridate)
```


## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 

```{r}
floor_date(today(), unit = "year") + months(0:11)
```

Write a function that given your birthday (as a date), returns how old you are in years.

```{r}
get_age <- function(birthday) {
  span=interval(birthday,today())
  floor(as.numeric(as.duration(span), "years"))
}
birthday <- ymd(19970619)
get_age(birthday)
```


Write a function that given your birthday, returns the day of the week you were born on. 

```{r}
get_day <- function(birthday) {
  wday(birthday,label=TRUE)
}
birthday <- ymd(19970619)
get_day(birthday)
```


## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)

```{r}
library(stringr)
devtools::install_github("VerbalExpressions/RVerbalExpressions")
library(RVerbalExpressions)
```

regular expressions

```{r}
word_list <- stringr::words
str_view(stringr::words, ".......", match = TRUE)
```

rverbalexpressions

```{r}
word_list <- stringr::words
seven_letter <-rx() %>%
  rx_start_of_line() %>%
  rx_word_char() %>% 
  rx_repeat_previous(7) %>%
  rx_anything() %>% 
  rx_end_of_line()
str_view(word_list,seven_letter,match=TRUE)
```

## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)

regular expressions

```{r}
index=str_detect(word_list, "^[^aeiou]*$")
word_list[index]
```

rverbalexpressions

```{r}
word_list <- stringr::words
only_consonants <-rx() %>%
  rx_start_of_line() %>% 
  rx_anything_but("aeiou") %>% 
  rx_end_of_line()

word_list[str_detect(word_list,only_consonants)]
```

Empirically verify the rule “i before e except after c”.

"I before E, except after C" is a mnemonic rule of thumb for English spelling. If one is not sure whether a word is spelled with the sequence ei or ie, the rhyme suggests that the correct order is ie unless the preceding letter is c, in which case it is ei. For example: ie in believe, fierce, collie, die, friend.

Thus, the spelling of cie will break this rule

regular expressions

```{r}
index=str_detect(word_list, "cie")
word_list[index]
```

The word "science" "society" break the rule “i before e except after c”.

rverbalexpressions

```{r}
ie_rule <-rx() %>%
  rx_find("cie")
  
word_list[str_detect(word_list,ie_rule)]
```

The word "science" "society" break the rule “i before e except after c”.

Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.

regular expressions

```{r}
x <- c("123-456-7890","123.456.7890","(123)456-7890")
```

format like 123-456-7890 or 123.456.7890

```{r}
x[str_detect(x, "^\\d{3}[-.]\\d{3}[-.]\\d{4}$")]
```

format like (123)456-7890

```{r}
x[str_detect(x,'^(\\()\\d{3}(\\))\\d{3}(-)\\d{4}$')]
```

rverbalexpressions

```{r}
x <- c("123-456-7890", "(123)456-7890","123.456.7890")
```

format like 123-456-7890 or 123.456.7890

```{r}
telrx1 <-rx() %>%
  rx_start_of_line() %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-.") %>%
  rx_digit() %>% 
  rx_repeat_previous(4) %>%
  rx_end_of_line()

x[str_detect(x,telrx1)]
```


format like (123)456-7890

```{r}
telrx2 <-rx() %>%
  rx_start_of_line() %>%
  rx_find("(") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_find(")") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_find("-") %>% 
  rx_digit() %>% 
  rx_repeat_previous(4) %>%
  rx_end_of_line()

x[str_detect(x,telrx2)]
```


