---
title: "Part 2"
output: html_notebook
---

1. Describe the data and the problem


```{r libraries}
library(readr)
library(assertr)
library(tidyverse)
library(lubridate)
library(janitor)
```

Problem: Given a list of users along with their demographics, web session records, and some summary statistics, we can build a model to predict Airbnb user destination for first booking. 

All the users in this dataset are from the USA.

```{r load data}
dest <- read_csv("train_users_2.csv")
dest <- dest %>% clean_names()
```


```{r dimension}
dim(dest)
```

The training data had the demographic and session information for 213451 users. It contains 16 variables in this data set.

```{r variable names}
names(dest)
```

date_account_created: the date of account creation

timestamp_first_active: timestamp of the first activity, note that it can be earlier than date_account_created or date_first_booking because a user can search before signing up

date_first_booking: date of first booking

signup_flow: the page a user came to signup up from

language: international language preference

affiliate_channel: what kind of paid marketing

affiliate_provider: where the marketing is e.g. google, craigslist, other

first_affiliate_tracked: whats the first marketing the user interacted with before the signing up

country_destination: the target variable to predict


```{r first device type}
dest %>% 
  distinct(first_device_type)
```

 Users can use the web application or the android/iOS application.


```{r signup method}
dest %>% 
  distinct(signup_method)
```

User can sign up via facebook, goole account or basic method.


```{r country destination}
dest %>% 
  distinct(country_destination)
```

There are 12 possible outcomes of the destination country: 'US'-USA, 'FR'-France, 'CA'-Canada, 'GB'-Great Britain, 'ES'-Spain, 'IT'-Italy, 'PT'-Portugal, 'NL'-Netherlands,'DE'-Denmark, 'AU'-Australia, 'NDF' (no destination found), and 'other'. 

'NDF' is different from 'other' because 'other' means there was a booking, but is to a country not included in the list, while 'NDF' means there wasn't a booking.


2. Read in and check data

**Data Type for Each Column**

we could check the data type for each column using head()

```{r data type}
head(dest)
```

**gender**

```{r gender}
dest %>% 
  distinct(gender)
```

For "-unknown", it should be considered as missing values in gender

**date_first_booking**

```{r NA in date first booking}
dest %>%
  verify(!is.na(date_first_booking))
```

There are 124,543 NA in date_first_booking. Thus, about 58% users didn't book a trip to any destination yet.

```{r NDF in country destination}
dest %>% 
  filter(country_destination=="NDF")
```

The number of users whose country destination is "NDF" is 124543, which is consistent with NA in date_first_booking. Thus, in the predict problem, we could predict all destinations to be NDF if data_first_booking is NA.

**age**

```{r NA in age}
dest %>%
  verify(!is.na(age))
```

There are 87990 missing values in age.

```{r extreme values in age}
dest %>%
  assert(within_bounds(0,120), age)
```

There are 781 extreme values in age


3. Clean up the data. 

**timestamp_first_active**

we can transform timestamp to POSIXct objects

```{r timestamp}
dest <- dest %>%
  mutate(timestamp_first_active=ymd_hms(as.character(dest$timestamp_first_active)))
```

**gender**

change all the "-unknown" in gender to NA

```{r modify gender}
dest <- dest %>% 
  mutate(gender=ifelse(gender=="-unknown-",NA,gender))
```


**signup method**

change signup method to factor and convert from category to numeric

```{r change signup method to factor}
dest <- dest %>% 
  mutate(signup_method =factor(signup_method,labels=1:3))
```

Thus, in the factor, basic is set to be 1, facebook is set to be 2 and google is set to be 3

**language**

change language to factor

```{r change language method to factor}
dest <- dest %>% 
  mutate(language =factor(language))
```

**first browser**

change all the "-unknown-" in first browser to NA

```{r modify first browser}
dest <- dest %>% 
  mutate(first_browser=ifelse(first_browser=="-unknown-",NA,first_browser))
```

**country destination**

change country_destination to factor

```{r change country destination to factor}
dest <- dest %>% 
  mutate(country_destination =factor(country_destination))
```

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*


4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

**function 1**

Given a month, some countries are more likely to be visited owing to seasonality in terms of weather/festivals. The travel destination for different countries could depend on the month. Given a month, some countries are more likely to be visited owing to seasonality in terms of weather/festivals.

```{r function1}
calc_month <- function (df,var) {
  df %>% 
    mutate(month=months({{var}}))
}

#test
dest %>% 
  calc_month(date_first_booking) %>% 
  select(date_first_booking,month,everything())
```

**function 2**

```{r histogram of age}
dest_new <- dest[!is.na(dest$date_first_booking) & dest$age<120 & !is.na(dest$age),]
hist(dest_new$age,xlab="age",main="histogram of user age")
```

From this histogram, we could see that most user that actually booked a trip is under 40, thus we could add a dummy variable to indicate if the age is under 40 or not. Let 1 be age under 40 and 0 be age above 40.


```{r function2}
age_dummy <- function (df,var) {
  df %>% 
    mutate(age_under_40=as.integer({{var}} <=40))
}

#test
dest %>% 
  age_dummy(age) %>% 
  select(age,age_under_40,everything())
```

**function 3**
The absence of date_first_booking means the destination is NDF(no destination found), thus we could add a column to indicate if there is a booking record. Then in prediction, we could eliminate the entries without booking record, and predicted the output, to be NDF.

```{r function3}
booking_record <- function (df,var) {
  df %>% 
    mutate(booking_or_not=case_when(
      is.na({{var}}) ~ 0,
      TRUE ~ 1)
    ) 
}

#test
dest %>% 
  booking_record(date_first_booking) %>% 
  select(date_first_booking,booking_or_not,everything())
```

**function 4**

The date first booking on which day of week will also affect the travel destination.

```{r}
weekday <-function(df,var){
  df %>%
  mutate(weekday = wday({{var}},label=TRUE))
}

##test
dest %>% 
  weekday(date_first_booking) %>% 
  select(date_first_booking,weekday,everything())
```


5. Prepare the data for modeling

```{r prepare data}
dest_prepare <- dest %>% 
  calc_month(date_first_booking) %>%
  age_dummy(age) %>%
  booking_record(date_first_booking) %>%
  weekday(date_first_booking) %>% 
  select(id,month,weekday,booking_or_not,gender,age_under_40,signup_method,language,first_browser,country_destination)

dest_prepare
```

```{r}
dim(dest_prepare)
```

```{r}
names(dest_prepare)
```

The prepared data contains 10 variables and 213451 observations.